---
title: "AIH_WGCNA"
author: "Arielle Klepper"
date: "9/23/2018"
output: html_document
---

## WGCNA - genes
loading packages needed for the analysis and then generating the gene counts and ensuring genes OK

```{r}

library("WGCNA")

#Turning vsd data from an S4 object into a data frame 
matrix_vsd <- assay(vsd)

#sawpping so that samples are row data and not column data with the transpose function 
t_matrix_vsd <- t(matrix_vsd)

#Flagging genes with too many missing values
##allOK is a column in the S4 data object to examine which genes meet the criteria; if result is TRUE, than genes meet criteria
gsg <- goodSamplesGenes(t_matrix_vsd, verbose = 3)
gsg$allOK

```

## Sample Clustering 
Gene expression data are then clustered by sample using sample data to check for outliers

```{r}

hc_matrix_vsd <- hclust(dist(t_matrix_vsd), method = "average")
sizeGrWindow(12,9)
par(cex = 0.6)
par(mar = c(0,4,2,0))
plot(hc_matrix_vsd, main = "sample clustering to detect outliers", sub="", xlab="", cex.lab=1.5, cex.axis=1.5, cex.main = 2)

```

## Reading in metadata
Reading in metadata written from filtered DESeq2 file and then format correctly for analysis 

```{r}



```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}

```


```{r}

```


```{r}

```


```{r}

```

