---
title: "Random Forest Model"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE}
library(varSelRF)
#set.seed(144681)
library(stringr)
library(knitr)
library(edgeR)
load("~/Documents/Informatics/AIH/github/AIH-Project/AIH-metadata/RandomForestData.RData")
```

##Using *varSelRF* package for variable selection using random forest

https://cran.r-project.org/web/packages/varSelRF/varSelRF.pdf

I normalized the pre-filtered gene counts of the 92 AIH and healthy patients (no liver transplants, no outliers and no complex cases) using cpm() function of EdgeR, log = TRUE.

I defined the two groups as AIH and healthy. 

After this, I ran the random forest model with differing standard deviations, starting at 2 and subtracting 0.25 in every loop. As the standard deviation became less stringent (lower), the number of genes increased. I recorded the genes in a dataframe.

```{r message=FALSE, warning=FALSE, include=TRUE, paged.print=FALSE}
set.seed(791638)

# load in genecounts and metadata
genecounts_rf <- genecountspc_filt
metadata_rf <- metadata_filt

# normalize gene counts
genecounts_filt_cpm <- cpm(genecountspc_filt, log = TRUE)

# set up the column of interest, remove empty levels
metadata_rf$factors <- droplevels.factor(metadata_filt$case_hl_du)

#declare the factors for random forest model (AIH vs healthy)
RF_factors <- metadata_rf$factors


RF_results <-data.frame(seed = integer(), stddev = integer(), num.genes = integer(), genes = character(), genes_ensembl = character())
seeds <- sample(1:1000000, 10, replace = FALSE)

for (i in seq(1,10)) {
  
  
set.seed(seeds[i])
  
#initialize data frame, standard deviation, number of genes
stddev = 2
num.genes = 0  
  #run random forest until I have more than 50 genes in a group
  while (num.genes < 50) {
  
  #random forest command
  varselRF.AIH <- varSelRF(t(genecounts_filt_cpm), as.factor(RF_factors), c.sd = stddev, mtryFactor = 1, ntree = 5000, ntreeIterat = 2000, vars.drop.num = NULL, vars.drop.frac = 0.2, whole.range = FALSE, recompute.var.imp = FALSE, verbose = TRUE, returnFirstForest = TRUE, fitted.rf = NULL, keep.forest = TRUE)
  
  #store data into data frame
  genes = genemap[match(varselRF.AIH$selected.vars, genemap$ensembl_gene_id),]$hgnc
  genes_ensembl = varselRF.AIH$selected.vars
  num.genes = varselRF.AIH$best.model.nvars
  genes_t <- data.frame(t(c(i, stddev, num.genes, paste(unlist(genes), collapse=', '),paste(unlist(genes_ensembl), collapse=', '))))
  colnames(genes_t) <- c("seed","stddev","num.genes","genes")
  RF_results<-rbind(RF_results,genes_t)
  
  #reduce standard deviation by 0.25
  stddev = stddev - 0.25
  
  }
}


```

```{r}
knitr::kable(RF_results)
write.c(RF_results,file = "RandomForest_12seeds_AIHvHealthy_021519")
```

