---
title: "AIH_WGCNA"
author: "Arielle Klepper"
date: "9/23/2018"
output: html_document
---

## WGCNA - genes
loading packages needed for the analysis and then generating the gene counts and ensuring genes OK

```{r}
biocLite("robustbase")
biocLite("pcaPP")
library("BiocInstaller")
biocLite("WGCNA")


library("WGCNA")
library("GO.db")
library("AnnotationDbi")
library("org.Hs.eg.db")
biocLite("anRichmentMethods")
library("anRichmentMethods")
library("anRichment")
library("XML")
library("dplyr")
library("TxDb.Hsapiens.UCSC.hg19.knownGene")

```

```{r}
setwd("~/Documents/Informatics/AIH/github/AIH-Project/DESeq2-R-Scripts/")

#Reading in expression data
t_matrix_vsd <- read.csv("VSDNormalized_AIH_filt_4_bydiagnosis.csv", row.names = 1)

#Flagging genes with too many missing values
##allOK is a column in the S4 data object to examine which genes meet the criteria; if result is TRUE, than genes meet criteria
gsg <- goodSamplesGenes(t_matrix_vsd, verbose = 3)
gsg$allOK
```

## Sample Clustering 
Gene expression data are then clustered by sample using sample data to check for outliers

```{r}
setwd("~/Documents/Informatics/AIH/github/AIH-Project/AIH metadata/")

#hc matrix clustering
hc_matrix_vsd <- hclust(dist(t_matrix_vsd), method = "ward.D2")
sizeGrWindow(12,9)
par(cex = 0.6)
par(mar = c(0,4,2,0))

#plotting hc data and then writing it to jpeg file
plot(hc_matrix_vsd, main = "h clustering, ward.D2", sub="", xlab="", cex.lab=1.5, cex.axis=1.5, cex.main = 2) 


```


## Reading in metadata
Reading in metadata written from filtered DESeq2 file and then format correctly for analysis 

```{r}
setwd("~/AIH-Project/AIH metadata/data")
AIH_metadata <- read.csv("AIH_metadata_filt.csv", row.names = 1)

#Removing unneededc column data and merged duplicate row data
AIH_metadata <- AIH_metadata[-c(69, 11,71, 92, 25, 72, 24, 30, 59, 21) ,-c(6, 21)]

#Recasting all variables as numeric (required in this model)
AIH_metadata$case_hl_du <- as.numeric(AIH_metadata$case_hl_du)
AIH_metadata$response <- as.numeric (AIH_metadata$case_hl_du)
AIH_metadata$sex <- as.numeric(AIH_metadata$sex)
AIH_metadata$race <- as.numeric(AIH_metadata$race)
AIH_metadata$ethn <- as.numeric(AIH_metadata$ethn)
AIH_metadata$aih_type <- as.numeric(AIH_metadata$aih_type)
AIH_metadata$on_tx <- as.numeric (AIH_metadata$on_tx)
AIH_metadata$response <- as.numeric (AIH_metadata$response)
AIH_metadata$relapse <- as.numeric (AIH_metadata$relapse)
AIH_metadata$decomp <- as.numeric(AIH_metadata$decomp)
AIH_metadata$lt <- as.numeric(AIH_metadata$lt)
AIH_metadata$liver_death <- as.numeric (AIH_metadata$liver_death)
AIH_metadata$dup <- as.numeric(AIH_metadata$dup)
AIH_metadata$F03_F4 <- as.numeric(AIH_metadata$F03_F4) 
AIH_metadata$plate <- as.numeric(AIH_metadata$plate)


```



## Re-clustering expression data w/ colors for clin data
Renaming to sample names of datExpr (for gene expression) and datTraits
```{r}
#renaming per tutorial code names to correspond to subsequent code
datExpr <- t_matrix_vsd
datTraits <- AIH_metadata

#traits as colors w/ dendogram
traitColors = numbers2colors(datTraits, signed = FALSE)
plotDendroAndColors(hc_matrix_vsd, traitColors, groupLabels = names(datTraits), main = "sample dendogram and trait heatmap")
```

## Chosing a soft thresholidng power and viewing network topology

```{r}

# Choose a set of soft-thresholding powers
powers <- c(c(1:10), seq(from = 12, to=20, by=2))

# Call the network topology analysis function - the below gives an error
sft <- pickSoftThreshold(datExpr, powerVector = powers, verbose = 5)

# Plot the results:
sizeGrWindow(9, 5)
par(mfrow = c(1,2))
cex1 = 0.9

# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"))
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red")

# this line corresponds to using an R^2 cut-off of h
abline(h=0.90,col="red")

# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")

```


# Step-by-step construction of the gene network and identification of modules

```{r}

##Stepwise code 

#Co-expression similarity and adjacency
softPower = 6
adjacency = adjacency(datExpr, power = softPower)

# Topological Overlap Matrix (TOM)
TOM = TOMsimilarity(adjacency)
dissTOM = 1-TOM

#Clustering using TOM
# Call the hierarchical clustering function
geneTree = hclust(as.dist(dissTOM), method = "average")
# Plot the resulting clustering tree (dendrogram)
sizeGrWindow(12,9)
plot(geneTree, xlab="", sub="", main = "Gene clustering on TOM-based dissimilarity",
labels = FALSE, hang = 0.04)

# We like large modules, so we set the minimum module size relatively high:
minModuleSize = 30;
# Module identification using dynamic tree cut:
dynamicMods = cutreeDynamic(dendro = geneTree, distM = dissTOM,
deepSplit = 2, pamRespectsDendro = FALSE,
minClusterSize = minModuleSize);
table(dynamicMods)

# Convert numeric lables into colors
dynamicColors = labels2colors(dynamicMods)
table(dynamicColors)
# Plot the dendrogram and colors underneath
sizeGrWindow(8,6)
plotDendroAndColors(geneTree, dynamicColors, "Dynamic Tree Cut",
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05,
main = "Gene dendrogram and module colors")

#Merging of modules whose expression profiles are very similar
# Calculate eigengenes
MEList = moduleEigengenes(datExpr, colors = dynamicColors)
MEs = MEList$eigengenes
# Calculate dissimilarity of module eigengenes
MEDiss = 1-cor(MEs);
# Cluster module eigengenes
METree = hclust(as.dist(MEDiss), method = "average");
# Plot the result
sizeGrWindow(7, 6)
plot(METree, main = "Clustering of module eigengenes",
xlab = "", sub = "")
MEDissThres = 0.25
# Plot the cut line into the dendrogram
abline(h=MEDissThres, col = "red")
# Call an automatic merging function
merge = mergeCloseModules(datExpr, dynamicColors, cutHeight = MEDissThres, verbose = 3)
# The merged module colors
mergedColors = merge$colors;
# Eigengenes of the new merged modules:
mergedMEs = merge$newME


#Replotting dendogram w clusters
sizeGrWindow(12, 9)
#pdf(file = "Plots/geneDendro-3.pdf", wi = 9, he = 6)
plotDendroAndColors(geneTree, cbind(dynamicColors, mergedColors),
c("Dynamic Tree Cut", "Merged dynamic"),
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05)
#dev.off()


# Rename to moduleColors
moduleColors = mergedColors

# Construct numerical labels corresponding to the colors
colorOrder = c("grey", standardColors(50));
moduleLabels = match(moduleColors, colorOrder)-1;
MEs = mergedMEs

# Save module colors and labels for use in subsequent parts
save(MEs, moduleLabels, moduleColors, geneTree, file = "AIH-networkConstruction-stepByStep.RData")

```


```{r}

```

#Relating modules to external information and identifying important genes
Eg metadata
```{r}

# Define numbers of genes and samples
nGenes = ncol(datExpr)
nSamples = nrow(datExpr)

# Recalculate MEs with color labels
MEs0 = moduleEigengenes(datExpr, moduleColors)$eigengenes
MEs = orderMEs(MEs0)
moduleTraitCor = cor(MEs, datTraits, use = "p")
moduleTraitPvalue = corPvalueStudent(moduleTraitCor, nSamples)

#Graph color coding associations by correlation value
sizeGrWindow(10,6)
# Will display correlations and their p-values
textMatrix = paste(signif(moduleTraitCor, 2), "\n(",
signif(moduleTraitPvalue, 1), ")", sep = "")
dim(textMatrix) = dim(moduleTraitCor)
par(mar = c(6, 8.5, 3, 3))
# Display the correlation values within a heatmap plot
labeledHeatmap(Matrix = moduleTraitCor,
xLabels = names(datTraits),
yLabels = names(MEs),
ySymbols = names(MEs),
colorLabels = FALSE,
colors = greenWhiteRed(50),
textMatrix = textMatrix,
setStdMargins = FALSE,
cex.text = 0.5,
zlim = c(-1,1),
main = paste("Module-trait relationships"))


```

#Annotating modules to assess significance 
Using Bioconductor default package to annotate genes

```{r}

#########Changing human gene names to entrez
entrez <- convert2entrez(organism = "human", symbol = colnames(datExpr))

# Get the corresponding Locuis Link IDs
allLLIDs = entrez

# $ Choose interesting modules
intModules = c("brown", "blue", "purple", "yellow", "turquoise")

# Select module probes
for (module in intModules)
{
modGenes = (moduleColors == module)
# Get their entrez ID codes
modLLIDs = allLLIDs[modGenes]
# Write them into a file
WGCNA_GO_analysis = paste("LocusLinkIDs-", module, ".txt", sep="");
write.table(as.data.frame(modLLIDs), file = fileName,
row.names = FALSE, col.names = FALSE)
}

# As background in the enrichment analysis, we will use all probes in the analysis.
fileName = paste("LocusLinkIDs-all.txt", sep="")
write.table(as.data.frame(colnames(datExpr)), file = fileName,
row.names = FALSE, col.names = FALSE)
all

#GO enrichment analysis
GOenr = GOenrichmentAnalysis(moduleColors, allLLIDs, organism = "human", nBestP = 10)

#View signficant reuslts -- this is the best table to explore
tab <- GOenr$bestPTerms[[4]]$enrichment

GOcollection = buildGOcollection(organism = "human")


```



```{r}

```


