---
title: "AIH_WGCNA"
author: "Arielle Klepper"
date: "9/23/2018"
output: html_document
---

## WGCNA - genes
loading packages needed for the analysis and then generating the gene counts and ensuring genes OK

```{r}

library("BiocInstaller")


library("WGCNA")
library("GO.db")
library("AnnotationDbi")
library("org.Hs.eg.db")
#library("anRichmentMethods")
#library("anRichment")
library("XML")
library("dplyr")

```

```{r}
setwd("~/Documents/Informatics/AIH/github/AIH-Project/AIH DESeq2 Output/")

#Reading in expression data
t_matrix_vsd <- read.csv("../AIH DESeq2 Output/VSDNormalized_case_control_minus67and94_101618.csv", row.names = 1)

#Flagging genes with too many missing values
##allOK is a column in the S4 data object to examine which genes meet the criteria; if result is TRUE, than genes meet criteria
#gsg <- goodSamplesGenes(t_matrix_vsd, verbose = 3)
#gsg$allOK
```

## Sample Clustering 
Gene expression data are then clustered by sample using sample data to check for outliers

```{r}
#setwd("~/Documents/Informatics/AIH/github/AIH-Project/AIH metadata/")

#hc matrix clustering
hc_matrix_vsd <- hclust(dist(t_matrix_vsd), method = "ward.D2")

sizeGrWindow(12,9)
par(cex = 0.6)
par(mar = c(0,4,2,0))
?hclust

#plotting hc data and then writing it to jpeg file
plot(hc_matrix_vsd, main = "h clustering, ward.D2", sub="", xlab="", cex.lab=1.5, cex.axis=1.5, cex.main = 2) 



```


## Reading in metadata
Reading in metadata written from filtered DESeq2 file and then format correctly for analysis 

```{r}
#setwd("~/AIH-Project/AIH metadata/data")
AIH_metadata <- read.csv("../AIH metadata/AIH_metadata_firstpass_ALedits.csv")

#Removing unneeded column data and merged duplicate row data
#AIH_metadata <- AIH_metadata[-c(72, 11,74,96,27,75,26,32,61,23,18,22, 67, 94),]
AIH_metadata <- AIH_metadata[-c(9,19,29,39,49,59,69,79,89,99,18,22, 67, 94),]

AIH_metadata
#Recasting all variables as numeric (required in this model)
AIH_metadata$case_hl_du <- as.numeric(AIH_metadata$case_hl_du)
AIH_metadata$response <- as.numeric (AIH_metadata$case_hl_du)
AIH_metadata$sex <- as.numeric(AIH_metadata$sex)
AIH_metadata$race <- as.numeric(AIH_metadata$race)
AIH_metadata$ethn <- as.numeric(AIH_metadata$ethn)
AIH_metadata$aih_type <- as.numeric(AIH_metadata$aih_type)
AIH_metadata$on_tx <- as.numeric (AIH_metadata$on_tx)
AIH_metadata$response <- as.numeric (AIH_metadata$response)
AIH_metadata$relapse <- as.numeric (AIH_metadata$relapse)
AIH_metadata$decomp <- as.numeric(AIH_metadata$decomp)
AIH_metadata$lt <- as.numeric(AIH_metadata$lt)
AIH_metadata$liver_death <- as.numeric (AIH_metadata$liver_death)
AIH_metadata$du <- as.numeric(AIH_metadata$du)
AIH_metadata$F03_F4 <- as.numeric(AIH_metadata$F03_F4) 
AIH_metadata$spl_plate <- as.numeric(AIH_metadata$spl_plate)
AIH_metadata$dt_isl <- as.numeric(AIH_metadata$dt_isl)
AIH_metadata$age <- cut(as.numeric(AIH_metadata$age), 3, labels = 1:3)
length(AIH_metadata$age)



```

```{r}
library("factoextra")
install.packages("FactoMineR")
library("FactoMineR")
library (fpc)
res <- hcut(dist(t_matrix_vsd), k = 8, stand = TRUE, hc_method = "ward.D2")
res$cluster

clusplot(res$data, res$cluster, color=FALSE, col.p=c("blue","red"),shade=FALSE, plotchar = FALSE,
  	labels=1, lines=0)

HCPC(pca, nb.clust = 0, iter.max = 10, min = 3, max = NULL, graph = TRUE)

idx<-match(res$labels,AIH_metadata$aasld_id)
caseidx<- AIH_metadata$case_hl_du[idx]

res$color = numbers2colors(caseidx, signed = FALSE)
dendr$color <- str_replace(dendr$color,"#FFFFFF", "#FF2222") 

pca <- prcomp(dist(t_matrix_vsd))

##Formatting PCA data into data frames for entry into ggplot 2
pcadf <- data.frame (sample = rownames (pca$x), x = pca$x[,1], y = pca$x[,2])


##Call to ggplot the new dataframes generated above
ggplot(data = pcadf, aes(x=x, y=y, label = sample)) +
  geom_text() +
  theme_bw() +
  ggtitle ("PCA by hiearchal clustering")

fviz_cluster(res, rect = TRUE, cex = 0.5,
         ellipse=TRUE, shape = "circle", geom = "point")
?fviz_cluster
plot(res)
fviz_contrib(res, choice = res$color, axes = 1)
fviz_pca_biplot()
my_data <- scale(dist(t_matrix_vsd))

fviz_nbclust(my_data, hclust)



K = 8
km = kmeans(t_matrix_vsd,centers=K)

X = t(scale(t_matrix_vsd,center=TRUE,scale=FALSE))
sv = svd(t(X))
U = sv$u
V = sv$v
D = sv$d
Z = t(X)%*%V

plot(Z[,1],Z[,2],col=km$cluster,type="n")
text(Z[,1],Z[,2],colnames(t_matrix_vsd),cex=.75,col=km$cluster)
cens = km$centers
points(cens%*%V[,1],cens%*%V[,2],col=1:K,pch=16,cex=3)

install.packages("cluster")
library(cluster)
clusplot(t_matrix_vsd, km$cluster, color=TRUE, shade=TRUE, 
         labels=2, lines=0)

library(cluster)
install.packages("HSAUR")
library(HSAUR)
?clusplot


ggplot(iris, aes(Petal.Length, Petal.Width, color = iris$cluster)) + geom_point()

```

```{r}
my_data <- scale(dist(t_matrix_vsd), center=TRUE, scale=FALSE)

fviz_nbclust(my_data, kmeans, method = "gap_stat")
?fviz_nbclust


km.res <- kmeans(my_data, 8, nstart = 1)
?kmeans

plot(km.res)

clusplot(my_data, km.res$cluster, color=FALSE, col.p=c("blue","red"),shade=FALSE, plotchar = FALSE,
  	labels=1, lines=0)

fviz_cluster(km.res, data = my_data,
             palette = c("#00AFBB","#2E9FDF", "#E7B800", "#FC4E07","#00AFCC","#2E9FCC", "#E7B821", "#FC4E13"),
             ggtheme = theme_minimal(),
             main = "Partitioning Clustering Plot",
             ellipse = FALSE,
             geom = "point"
             )


```



```{r}
library(ggplot2)
install.packages("ggdendro")
library(ggdendro)



dendr <- dendro_data(hc_matrix_vsd, type="rectangle") 
idx<-match(label(dendr)[,3],AIH_metadata$aasld_id)
caseidx<- AIH_metadata$case_hl_du[idx] 
dendr$color = numbers2colors(caseidx, signed = FALSE)
dendr$color <- str_replace(dendr$color,"#FFFFFF", "#FF2222") 


ggplot() + 
  geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend)) + 
  geom_text(data=label(dendr), aes(x=x, y=y, label=label, color =dendr$color, hjust=0), size=3) +
  coord_flip() + scale_y_reverse(expand=c(0.2, 0)) + 
  theme(axis.line.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_rect(fill="white"),
        panel.grid=element_blank()) +
  scale_color_discrete(name = "Condition", labels = c("Case", "Control"))


plateidx<- AIH_metadata$spl_plate[idx] 
dendr$color = numbers2colors(plateidx, signed = FALSE)
dendr$color <- str_replace(dendr$color,"#FFFFFF", "#FF2222") 


ggplot() + 
  geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend)) + 
  geom_text(data=label(dendr), aes(x=x, y=y, label=label, color =dendr$color, hjust=0), size=3) +
  coord_flip() + scale_y_reverse(expand=c(0.2, 0)) + 
  theme(axis.line.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_rect(fill="white"),
        panel.grid=element_blank()) +
  scale_color_discrete(name = "Library Prep Batch", labels = c("Plate 1", "Plate 2"))


rnabatch<- AIH_metadata$dt_isl[idx] 
dendr$color = numbers2colors(rnabatch, signed = FALSE)
dendr$color <- str_replace(dendr$color,"#FFFFFF", "#FF2222") 


ggplot() + 
  geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend)) + 
  geom_text(data=label(dendr), aes(x=x, y=y, label=label, color =dendr$color, hjust=0), size=3) +
  coord_flip() + scale_y_reverse(expand=c(0.2, 0)) + 
  theme(axis.line.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_rect(fill="white"),
        panel.grid=element_blank()) +
  scale_color_discrete(name = "RNA Batch", labels = c("Batch 1", "Batch 2", "Batch 3", "Batch 4"))

age<- AIH_metadata$age[idx] 

dendr$color = numbers2colors(as.numeric(age), signed = FALSE)
dendr$color <- str_replace(dendr$color,"#FFFFFF", "#FF2222") 

ggplot() + 
  geom_segment(data=segment(dendr), aes(x=x, y=y, xend=xend, yend=yend)) + 
  geom_text(data=label(dendr), aes(x=x, y=y, label=label, color =dendr$color, hjust=0), size=3) +
  coord_flip() + scale_y_reverse(expand=c(0.2, 0)) + 
  theme(axis.line.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.y=element_blank(),
        axis.title.y=element_blank(),
        panel.background=element_rect(fill="white"),
        panel.grid=element_blank()) +
  scale_color_discrete(name = "age", labels = c("20-39", "40-59", "60-79"))

```


## Re-clustering expression data w/ colors for clin data
Renaming to sample names of datExpr (for gene expression) and datTraits
```{r}
#ggplot color dendrogam

#renaming per tutorial code names to correspond to subsequent code
datExpr <- t_matrix_vsd
datTraits <- AIH_metadata$dt_isl

length (datTraits)
#traits as colors w/ dendogram
library("stringr")
?numbers2colors
traitColors = numbers2colors(datTraits, signed = FALSE)
traitColors <- str_replace(traitColors,"#FFFFFF", "#FF2222") 
?numbers2colors
hc_matrix_vsd
traitColors

unique(traitColors)
plotDendroAndColors(hc_matrix_vsd, traitColors, groupLabels = names(datTraits), main = "sample dendogram and trait heatmap")
```

## Chosing a soft thresholidng power and viewing network topology

```{r}

# Choose a set of soft-thresholding powers
powers <- c(c(1:10), seq(from = 12, to=20, by=2))

# Call the network topology analysis function - the below gives an error
sft <- pickSoftThreshold(datExpr, powerVector = powers, verbose = 5)

# Plot the results:
sizeGrWindow(9, 5)
par(mfrow = c(1,2))
cex1 = 0.9

# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
main = paste("Scale independence"))
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
labels=powers,cex=cex1,col="red")

# this line corresponds to using an R^2 cut-off of h
abline(h=0.90,col="red")

# Mean connectivity as a function of the soft-thresholding power
plot(sft$fitIndices[,1], sft$fitIndices[,5],
xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
main = paste("Mean connectivity"))
text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")

```


# Step-by-step construction of the gene network and identification of modules

```{r}

##Stepwise code 

#Co-expression similarity and adjacency
softPower = 6
adjacency = adjacency(datExpr, power = softPower)

# Topological Overlap Matrix (TOM)
TOM = TOMsimilarity(adjacency)
dissTOM = 1-TOM

#Clustering using TOM
# Call the hierarchical clustering function
geneTree = hclust(as.dist(dissTOM), method = "average")
# Plot the resulting clustering tree (dendrogram)
sizeGrWindow(12,9)
plot(geneTree, xlab="", sub="", main = "Gene clustering on TOM-based dissimilarity",
labels = FALSE, hang = 0.04)

# We like large modules, so we set the minimum module size relatively high:
minModuleSize = 30;
# Module identification using dynamic tree cut:
dynamicMods = cutreeDynamic(dendro = geneTree, distM = dissTOM,
deepSplit = 2, pamRespectsDendro = FALSE,
minClusterSize = minModuleSize);
table(dynamicMods)

# Convert numeric lables into colors
dynamicColors = labels2colors(dynamicMods)
table(dynamicColors)
# Plot the dendrogram and colors underneath
sizeGrWindow(8,6)
plotDendroAndColors(geneTree, dynamicColors, "Dynamic Tree Cut",
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05,
main = "Gene dendrogram and module colors")

#Merging of modules whose expression profiles are very similar
# Calculate eigengenes
MEList = moduleEigengenes(datExpr, colors = dynamicColors)
MEs = MEList$eigengenes
# Calculate dissimilarity of module eigengenes
MEDiss = 1-cor(MEs);
# Cluster module eigengenes
METree = hclust(as.dist(MEDiss), method = "average");
# Plot the result
sizeGrWindow(7, 6)
plot(METree, main = "Clustering of module eigengenes",
xlab = "", sub = "")
MEDissThres = 0.25
# Plot the cut line into the dendrogram
abline(h=MEDissThres, col = "red")
# Call an automatic merging function
merge = mergeCloseModules(datExpr, dynamicColors, cutHeight = MEDissThres, verbose = 3)
# The merged module colors
mergedColors = merge$colors;
# Eigengenes of the new merged modules:
mergedMEs = merge$newME


#Replotting dendogram w clusters
sizeGrWindow(12, 9)
#pdf(file = "Plots/geneDendro-3.pdf", wi = 9, he = 6)
plotDendroAndColors(geneTree, cbind(dynamicColors, mergedColors),
c("Dynamic Tree Cut", "Merged dynamic"),
dendroLabels = FALSE, hang = 0.03,
addGuide = TRUE, guideHang = 0.05)
#dev.off()


# Rename to moduleColors
moduleColors = mergedColors

# Construct numerical labels corresponding to the colors
colorOrder = c("grey", standardColors(50));
moduleLabels = match(moduleColors, colorOrder)-1;
MEs = mergedMEs

# Save module colors and labels for use in subsequent parts
save(MEs, moduleLabels, moduleColors, geneTree, file = "AIH-networkConstruction-stepByStep.RData")

```


```{r}

```

#Relating modules to external information and identifying important genes
Eg metadata
```{r}

# Define numbers of genes and samples
nGenes = ncol(datExpr)
nSamples = nrow(datExpr)

# Recalculate MEs with color labels
MEs0 = moduleEigengenes(datExpr, moduleColors)$eigengenes
MEs = orderMEs(MEs0)
moduleTraitCor = cor(MEs, datTraits, use = "p")
moduleTraitPvalue = corPvalueStudent(moduleTraitCor, nSamples)

#Graph color coding associations by correlation value
sizeGrWindow(10,6)
# Will display correlations and their p-values
textMatrix = paste(signif(moduleTraitCor, 2), "\n(",
signif(moduleTraitPvalue, 1), ")", sep = "")
dim(textMatrix) = dim(moduleTraitCor)
par(mar = c(6, 8.5, 3, 3))
# Display the correlation values within a heatmap plot
labeledHeatmap(Matrix = moduleTraitCor,
xLabels = names(datTraits),
yLabels = names(MEs),
ySymbols = names(MEs),
colorLabels = FALSE,
colors = greenWhiteRed(50),
textMatrix = textMatrix,
setStdMargins = FALSE,
cex.text = 0.5,
zlim = c(-1,1),
main = paste("Module-trait relationships"))


```

#Annotating modules to assess significance 
Using Bioconductor default package to annotate genes

```{r}

#########Changing human gene names to entrez
entrez <- convert2entrez(organism = "human", symbol = colnames(datExpr))

# Get the corresponding Locuis Link IDs
allLLIDs = entrez

# $ Choose interesting modules
intModules = c("brown", "blue", "purple", "yellow", "turquoise")

# Select module probes
for (module in intModules)
{
modGenes = (moduleColors == module)
# Get their entrez ID codes
modLLIDs = allLLIDs[modGenes]
# Write them into a file
WGCNA_GO_analysis = paste("LocusLinkIDs-", module, ".txt", sep="");
write.table(as.data.frame(modLLIDs), file = fileName,
row.names = FALSE, col.names = FALSE)
}

# As background in the enrichment analysis, we will use all probes in the analysis.
fileName = paste("LocusLinkIDs-all.txt", sep="")
write.table(as.data.frame(colnames(datExpr)), file = fileName,
row.names = FALSE, col.names = FALSE)
all

#GO enrichment analysis
GOenr = GOenrichmentAnalysis(moduleColors, allLLIDs, organism = "human", nBestP = 10)

#View signficant reuslts -- this is the best table to explore
tab <- GOenr$bestPTerms[[4]]$enrichment

GOcollection = buildGOcollection(organism = "human")


```



```{r}

```


